Using reference models in feature selection \vspace{.1in}

### 2019-12-04 paper/ref_approach.tex
minor cleaning

Reference models have been also used in non-Bayesian contexts, where
\cite{harrell2015regression} describes them as full models that can be
thought of as a ``gold standard'' (for a given application).  For
example, \cite{faraggi2001understanding} deal with the necessity of
identifying interpretable risk groups in the context of survival data
using neural networks, which typically perform very well in terms of
prediction, but whose covariates are difficult to be understood in
terms of relevance.  \cite{paul2008preconditioning}, using the term
preconditioning, explore approximating models fitting Lasso or
stepwise regression against consistent estimates $\hat{y}$ of a
reference model instead of the observed responses $y$.

@@

Blah blah

\subsection{Example of model selection with or without reference model}
\label{intro-example}

@@

\hypertarget{real-world-data}{%
\subsection{Body fat example part 2}\label{real-world-data}}

@@

\hypertarget{real-world-data}{%
\subsection{Body fat example part 3}\label{real-world-data}}

>>>>

Reference models have been also used in non-Bayesian contexts, where
\cite{harrell2015regression} describes them as full models that can be
thought of as a ``gold standard'' (for a given application).  For
example, \cite{faraggi2001understanding} deal with the necessity of
identifying interpretable risk groups in the context of survival data
using neural networks, which typically perform very well in terms of
prediction, but whose covariates are difficult to be understood in
terms of relevance.  \cite{paul2008preconditioning}, using the term
preconditioning, explore approximating models fitting Lasso or
stepwise regression against consistent estimates $\hat{y}$ of a
reference model instead of the observed responses $y$.
Whatever the terminology or applied statistical framework, reference
models offer a powerful approach to improving feature selection as we
will demonstrate in the present paper.

@@

In this section, we will provide an initial motivation and intuition 
for the use of reference models to improve feature selection procedures.
We will start with a case study that is repeatedly used throughout
the paper to illustrate the benefits of reference models before we dive deeper
into the theoretical reasons why reference models help in feature selection.

\subsection{Bodyfat example: Part 1}
\label{intro-example}

@@

\hypertarget{real-world-data}{%
\subsection{Body fat example: Part 2}\label{real-world-data}}

@@

\hypertarget{real-world-data}{%
\subsection{Body fat example: Part 3}\label{real-world-data}}
